### 2012-09-25 paper_sean/introduction.tex
changed figure caption for figure 1

% !TEX root =main.tex
Robots that can move around on legs can operate in a much wider range of environments than their wheeled counterparts. A downside is that designing gaits for legged robots is a difficult and time-consuming process for human engineers~\cite{strom1999legged,wettergreen1992gait}, and must be repeated every time a new robot is created or the design of an existing robot is changed~\cite{hornby2005autonomous}. 
Because of these difficulties in hand-designing gaits, scientists have investigated automatically producing gaits with machine learning or evolutionary algorithms, an approach that often produces better gaits than those created by human engineers~\cite{valsalam:mii,kohl:stone,hornby2005autonomous,hornby2003generative,yos:clune}. It has often been found that both machine-created and human-created gaits perform better if they are \emph{regular}, in that they have coordinated movements, such as left-right symmetry or front-back symmetry~\cite{valsalam:mii,clune2011performance,clune2009evolving,clune2009sensitivity}.
However, in most previous works, the experimenter has had to manually decide the regularities of the evolved gaits \cite{valsalam:mii,tellez,beer,raibert}. 
Such manual intervention is time consuming, requires expert knowledge, and adds constraints that may hurt performance.

>>>>

% !TEX root =main.tex
\figgp{quadratotWhiteBooties}{.45}{quadratot_simulator}{.45}{The QuadraTot robot platform on which gaits were evolved. \textbf{Left: } The physical robot, which is composed of 3-D printable and off-the-shelf components.
\textbf{Right: } The robot in the simulator. Figure adapted from from Glette et al. \cite{glette}.}

Robots that can move around on legs can operate in a much wider range of environments than their wheeled counterparts. A downside is that designing gaits for legged robots is a difficult and time-consuming process for human engineers~\cite{strom1999legged,wettergreen1992gait}, and must be repeated every time a new robot is created or the design of an existing robot is changed~\cite{hornby2005autonomous}. 
Because of these difficulties in hand-designing gaits, scientists have investigated automatically producing gaits with machine learning or evolutionary algorithms, an approach that often produces better gaits than those created by human engineers~\cite{valsalam:mii,kohl:stone,hornby2005autonomous,hornby2003generative,yos:clune}. It has often been found that both machine-created and human-created gaits perform better if they are \emph{regular}, in that they have coordinated movements, such as left-right symmetry or front-back symmetry~\cite{valsalam:mii,clune2011performance,clune2009evolving,clune2009sensitivity}.
However, in most previous works, the experimenter has had to manually decide the regularities of the evolved gaits \cite{valsalam:mii,tellez,beer,raibert}. 
Such manual intervention is time consuming, requires expert knowledge, and adds constraints that may hurt performance.
